### 2015-01-02 mcmc.tex
notes to self

\paragraph{Importance:}

\paragraph{Tempering:}

\paragraph{Nested:}

@@

Making this heuristic condition more precise...
Autocorrelation time is the premier tool...
How is Autocorrelation time defined?..
How is Autocorrelation time measured?..
Why is it is not a panacea?..

@@

The simplest proxy for autocorrelation time optimization is the \emph{acceptance fraction}.
If you are accepting almost all proposed steps, your step sizes are too small on average.
If you are accepting almost none, your step sizes are too large.
The Goldilocks value is around a half,
  with a strong argument floating around that it should be 0.234 for best performance\note{CITE GELMAN}.
In the burn-in phase (discussed below) of an MCMC run,
  it makes sense to track the acceptance ratio,
  and adjust the proposal distribution variance as you get acceptance ratios
  that are far from the Goldilocks ratio.
This process can be automated easily;
  such automation is part of many projects that use MCMC.

>>>>

\paragraph{Importance:}
... HOGG

\paragraph{Tempering:}
... HOGG

\paragraph{Nested:}
... HOGG

@@

...Making this heuristic condition more precise
...Autocorrelation time is the premier tool
...How is Autocorrelation time defined?
...How is Autocorrelation time measured?
...Why is it is not a panacea? ...estimators ...getting stuck in one mode

@@

The simplest heuristic proxy statistic for tuning is the \emph{acceptance fraction}.
If you are accepting almost all proposed steps, your step sizes are too small on average.
If you are accepting almost none, your step sizes are too large.
The Goldilocks value is around a quarter,
  with an argument floating around that it should be 0.234 for best performance\note{CITE GELMAN}
  (though you could never tune it precisely enough to warrant that third digit of accuracy).
In the burn-in phase (discussed below) of an MCMC run,
  it makes sense to track the acceptance ratio,
  and adjust the proposal distribution variance as you get acceptance ratios
  that are far from the Goldilocks ratio.
This process can be automated easily;
  such automation is part of many projects that use MCMC.
